Importance sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-02-17 draft_p2.tex
Removes dead code
Updates legend for dynamics_extremes and shear_asof_drag

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{timeseries_extremes/timeseries_extremes.png}
  \caption{Average drag timeseries in the vicinity of an extreme drag fluctuation at $t=t^{\star}$. The blue continuous line results from an average over the 104 extreme events sampled in the control run. This illustrates that extreme drag variations are very local in time, with a typical lifetime of one correlation time unit $\tau_c$.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{dynamics_extremes/dynamics_extremes.png}
\end{figure}

% \begin{figure}
%   \centering
%   \begin{minipage}{0.85\linewidth}
%     \begin{tabular}{c|c}
%     \subfloat[$f'_d = 11.6\sigma$]{\label{fig:top_4_events_vorticity_a}\includegraphics[width=0.4\linewidth]{event_95_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$f'_d = 11.2\sigma$]{\includegraphics[width=0.4\linewidth]{event_69_vort.png}} \\
%     \hline
%     \subfloat[$f'_d = 10.6\sigma$]{\includegraphics[width=0.4\linewidth]{event_53_vort.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$10\sigma$]{\includegraphics[width=0.4\linewidth]{event_20_vort.png}}
%     \end{tabular}
%   \end{minipage}
% \begin{minipage}[h]{0.1\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{scale_vorticity.png}
% \end{minipage}
% \caption{\label{fig:top_4_events_vorticity} Vorticity field at $t=t^{\star}$ for the four highest drag fluctuations in the timeseries. The corresponding drag timeseries can be found in figure~\ref{fig:extremes_timeseries}.
%   The high value for the drag results from the formation of a strong negative (red) vortex inducing a pressure drop at the base of the obstacle. The formation of such a structure is aided by important vorticity production at the bottom boundary of the obstacle coupled with the influence of positive vorticity in the vicinity of the base.}
% \end{figure}

% \begin{figure}
%   \centering
%   \begin{minipage}[h]{0.85\linewidth}
%     \begin{tabular}[h]{c|c}
%     \subfloat[$f'_d = 11.6\sigma$]{\label{fig:top_4_events_streamlines_a}\includegraphics[width=0.4\linewidth]{event_95_streamlines.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$f'_d = 11.2\sigma$]{\includegraphics[width=0.4\linewidth]{event_69_streamlines.png}} \\
%     \hline
%     \subfloat[$f'_d = 10.6\sigma$]{\includegraphics[width=0.4\linewidth]{event_53_streamlines.png}} \hspace{0.5cm} & \hspace{0.5cm} \subfloat[$f'_d = 10\sigma$]{\includegraphics[width=0.4\linewidth]{event_20_streamlines.png}} 
%   \end{tabular}
% \end{minipage}
% \begin{minipage}[h]{0.1\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{scale_density.png}
% \end{minipage}
% \caption{\label{fig:top_4_events_streamlines} Density field at $t=t^{\star}$ for the four highest drag fluctuations in the control simulation for \tf{2}. Recall that the density $\rho$ is proportional to the pressure $p$, following the ideal gas state equation $p=c_s^2\rho$. See chapter~\ref{chap:test_flows} and appendix~\ref{app:lbm}. Additionally, velocity streamlines are depicted, representing advection by the flow at $t=t^{\star}$, see note~\ref{note:streamlines}. Blue areas indicate areas of lower pressure while red regions indicate regions of higher pressure. The formation of a vortex very close to the base boundary leads to a strong pressure drop. The downstream vortices originating from the top boundary layer separation are clearly visible and constrain the formation of the base vortex to a region very close to the base boundary.}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.1\linewidth]{scale_vorticity.png}
%   \begin{tabular}[h]{cccc}
%     \subfloat[$t = t^{\star}-0.54\tau_c$]{\label{frame_a}\includegraphics[width=.2\linewidth]{animation_event_95_0035}} & \subfloat[$t = t^{\star}-0.5\tau_c$]{\label{frame_b}\includegraphics[width=.2\linewidth]{animation_event_95_0036}} &     \subfloat[$t = t^{\star}-0.46\tau_c$]{\label{frame_c}\includegraphics[width=.2\linewidth]{animation_event_95_0037}} &     \subfloat[$t = t^{\star}-0.44\tau_c$]{\label{frame_d}\includegraphics[width=.2\linewidth]{animation_event_95_0038}} \\
%     \subfloat[$t = t^{\star}-0.4\tau_c$]{\label{frame_e}\includegraphics[width=.2\linewidth]{animation_event_95_0039}} &     \subfloat[$t = t^{\star}-0.36\tau_c$]{\label{frame_f}\includegraphics[width=.2\linewidth]{animation_event_95_0040}} &     \subfloat[$t = t^{\star}-0.34\tau_c$]{\label{frame_g}\includegraphics[width=.2\linewidth]{animation_event_95_0041}} &     \subfloat[$t = t^{\star}-0.3\tau_c$]{\label{frame_h}\includegraphics[width=.2\linewidth]{animation_event_95_0042}} \\
%     \subfloat[$t = t^{\star}-0.26\tau_c$]{\label{frame_i}\includegraphics[width=.2\linewidth]{animation_event_95_0043}} &     \subfloat[$t = t^{\star}-0.24\tau_c$]{\label{frame_j}\includegraphics[width=.2\linewidth]{animation_event_95_0044}} &     \subfloat[$t = t^{\star}-0.2\tau_c$]{\label{frame_k}\includegraphics[width=.2\linewidth]{animation_event_95_0045}} &     \subfloat[$t = t^{\star}-0.16\tau_c$]{\label{frame_l}\includegraphics[width=.2\linewidth]{animation_event_95_0046}} \\
%     \subfloat[$t = t^{\star}-0.12\tau_c$]{\label{frame_m}\includegraphics[width=.2\linewidth]{animation_event_95_0047}} &     \subfloat[$t = t^{\star}-0.08\tau_c$]{\label{frame_n}\includegraphics[width=.2\linewidth]{animation_event_95_0048}} &     \subfloat[$t = t^{\star}-0.04\tau_c$]{\label{frame_o}\includegraphics[width=.2\linewidth]{animation_event_95_0049}} &     \subfloat[$t = t^{\star}$]{\label{frame_p}\includegraphics[width=.2\linewidth]{animation_event_95_0050}} \\
%   \end{tabular}
%   \caption{\label{fig:type_1_event}Flow dynamics corresponding to a particular type 1 event, which drag timeseries and flow fields at $t=t^{\star}$ are displayed in figures~\ref{fig:extremes_timeseries}, \ref{fig:top_4_events_vorticity} and~\ref{fig:top_4_events_streamlines}, respectively. In each frame the vorticity field is displayed, as well as the velocity streamlines, representing advection by the flow at each instant. See note~\ref{note:streamlines} for a discussion of streamlines.
%     The maximum of the drag is attained for $t=t^{\star}$ and corresponds to frame~\ref{frame_p}.  The sequence starts with a shear boundary layer forming over the top boundary of the obstacle (frames~\ref{frame_a} to~\ref{frame_d}). This boundary layer separates (frames~\ref{frame_e} to~\ref{frame_j}) and results in the formation of a large positive eddy in the vicinity of the base of the obstacle (frames~\ref{frame_k} and~\ref{frame_l}). In the meantime, frames~\ref{frame_j} to~\ref{frame_m} depict the formation of an attached strong shear layer at the bottom boundary. Eventually, frames~\ref{frame_n} to~\ref{frame_p} illustrate that this results in vorticity production very close to the base, aided by the large positive eddy originating from the top boundary layer separation.}
% \end{figure}

@@

Figure~\ref{fig:dynamics} illustrate the time evolution of the vorticity field, in the vicinity of the drag fluctuation, for the event depicted in figure~\ref{fig:illustr_density_streamlines}.
From $t^{\star}-0.4\tau_c$ to $t^{\star}-0.16\tau_c$, a strong negative eddy is generated along the bottom boundary layer of the obstacle and advected downstream by the mean flow.
This leads to a region of negative vorticity at roughly one obstacle length of the base of the obstacle, constraining the positive vorticity generated along the top boundary.
However, it can be seen in figure~\ref{fig:dynamics} that the positive vorticity only accumulates for a short duration.
The blocking negative vortex is in turn advected downstream, thus freeing the trapped positive vorticity.

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{shear_asof_drag/shear_asof_drag}
  \caption{\label{fig:shear_asof_drag}}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{timeseries_extremes/timeseries_extremes.png}
  \label{fig:timeseries_extremes}
  \caption{Average drag timeseries in the vicinity of an extreme drag fluctuation at $t=t^{\star}$. The blue continuous line results from an average over the 104 extreme events sampled in the control run. This illustrates that extreme drag variations are very local in time, with a typical lifetime of one correlation time unit $\tau_c$.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.8\linewidth]{dynamics_extremes/dynamics_extremes.png}
  \label{fig:vorticity_dynamics}
  \caption{Vorticity dynamics associated to an extreme fluctuation of the drag acting on the square obstacle at $t=t^{\star}$.}
\end{figure}

@@

Figure~\ref{fig:vorticity_dynamics} illustrate the time evolution of the vorticity field, in the vicinity of the drag fluctuation, for the event depicted in figure~\ref{fig:illustr_density_streamlines}.
From $t^{\star}-0.4\tau_c$ to $t^{\star}-0.16\tau_c$, a strong negative eddy is generated along the bottom boundary layer of the obstacle and advected downstream by the mean flow.
This leads to a region of negative vorticity at roughly one obstacle length of the base of the obstacle, constraining the positive vorticity generated along the top boundary.
However, it can be seen in figure~\ref{fig:vorticity_dynamics} that the positive vorticity only accumulates for a short duration.
The blocking negative vortex is in turn advected downstream, thus freeing the trapped positive vorticity.

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\linewidth]{shear_asof_drag/shear_asof_drag}
  \caption{\label{fig:shear_asof_drag} Evolution of the shear alongised the top or bottom boundary of the obsatcle as a function of the drag, for $t^{\star}-2\tau_c \leq t \leq t^{\star}-2\tau_c$. To each oneof the grey lines correspond a unique extreme event. The blue line is the average over the 104 extreme event sampled in the control run.  }
\end{figure}
